\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-14 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updated TPS manuscript

\bibitem{oksendal2013stochastic}
B.~Oksendal, \emph{Stochastic Differential Equations: An Introduction with Applications}, \emph{Springer Science \& Business Media}, 2013.

>>>>

\bibitem{oksendal2013stochastic}
B.~\O{}ksendal, \emph{Stochastic Differential Equations: An Introduction with Applications}, \emph{Springer Science \& Business Media}, 2013.
